Combined Task and Motion Planner through an Interface Layer

### 2015-04-16 documentation/draft.tex
added documentation section about continuous variables

Simple example walkthrough:

@@

-continuous variables represented symbolically

@@

@@

@@

>>>>

\subsection{Simple Example Walkthrough}

@@

One of the key insights of this paper is that continuous variables can be referenced symbolically in the task planner.  
For instance, consider the pose of the robot: this is a continuous, geometric state.  However, the task planner only keeps track of poses symbolically.  
The task planner knows that there is some GPFG\_obj\_1 -- a Gripper Pose For Grasping -- for object 1, and it doesn't really care what that pose is, so long as it exists.  
The task planner reasons over a variety of these symbolic variables, corresponding to poses and trajectories.  
The motion planner and pose generators take these symbolic variables and associate them with corresponding real locations and motions in the world.  
This is the key insight which allows the task planner to reason about continuous variables without discretizing.

@@

veronica can probably write this section

@@

Bianca will finish writing this section and the corresponding subsections tomorrow

@@

\subsection{API and Interfaces}

Alex should write this section, probably mostly the same as the stuff he's writing for the readme/etc.
